### 2019-06-08 2-Chapters/6-Chapter/nonstatbandits.git/NonStatB.tex
Done, I changed := to \overset{.}{=}

A \emph{piece-wise stationary bandit model} is characterized by a set of $K$ arms.
A (random) stream of rewards $(Y_{k,t})_{t\in\N^*}$ is associated to each arm $k \in [K]$. We assume that the rewards are bounded, and without loss of generality we assume that $Y_{k,t} \in [0,1]$.
We denote by $\mu_k(t) :=  \bE[Y_{k,t}]$ the mean reward of arm $k$ at round $t$. At each round $t$, a decision maker has to select an arm $A(t)\in[K]$, based on past observation and receives the corresponding reward $r(t) = Y_{A(t),t}$.
At time $t$, we denote by $k_t^*$ an arm with maximal expected reward, \ie, $\mu_{k_t^*}(t) = \max_k \mu_k(t)$, called an optimal arm (possibly not unique).

@@

In the piece-wise \iid{} model, we furthermore assume that there is a (relatively small) number of \emph{breakpoints}, denoted by $\Upsilon_T:=\sum_{t=1}^{T-1} \indic\left(\exists k\in[K]: \mu_k(t) \neq \mu_k(t+1)\right)$.
If we denote $\tau^{(0)} = 0$, we define the $i$-th breakpoint recursively by
$\tau^{(i)} = \inf\{t > \tau^{(i-1)} : \exists k : \mu_k(t) \neq \mu_k(t+1)\}$.
%
Hence for $t\in[\tau^{(i)} + 1,\tau^{(i+1)}]$, that is on any stationary segments, the rewards $(Y_{k,t})$ associated to each arm $k$ are \iid{} (hence the name of \emph{piece-wise stationary} problems).

@@

We define the \emph{number of change-points} on arm $k$,
$\NCk := \sum_{t=1}^{T-1} \indic\left(\mu_k(t) \neq \mu_k(t+1)\right)$,
for which it clearly holds that
$\NCk \leq \Upsilon_T$, but there can be an arbitrary difference between these two quantities for some arms. Letting $C_T := \sum_{k=1}^K \NCk$ be the total number of change-points on the arms, one can have $C_T \in \{ \Upsilon_T, \dots, K\Upsilon_T \}$.
We illustrate the two extreme cases in problems $1$ and $2$ presented in Figures~\ref{fig:6:Problem_1} and \ref{fig:6:Problem_2} below.

@@

If the samples $(X_t)$ were all drawn from a Bernoulli distribution, this change-point detection problem introduced above would reduce to a parametric sequential test of
$\cH_0 : (\exists \mu_0: \forall i\in\N, X_i \ \overset{\text{i.i.d.}}{\sim} \ \cB(\mu_0))$,
against the alternative
$\cH_1 : (\exists \mu_0 \neq \mu_1, \tau \in \N^*: \ \  X_1, \dots, X_\tau \ \overset{\text{i.i.d.}}{\sim} \ \cB(\mu_0) \ \ \text{and} \ \ X_{\tau+1}, X_{\tau+2}, \dots \ \overset{\text{i.i.d.}}{\sim} \ \cB(\mu_1))$.
%
The Generalized Likelihood Ratio statistic for this test is defined by
\begin{equation}\label{eq:6:firstDefGLRT}
    \GLR(n) :=\frac{\sup\limits_{\mu_0,\mu_1,\tau < n}\ell(X_1, \dots, X_n ; \mu_0,\mu_1,\tau)}{\sup\limits_{\mu_0}\ell(X_1, \dots, X_n ; \mu_0)},
\end{equation}
%
where $\ell(X_1, \dots, X_n ; \mu_0)$ and $\ell(X_1, \dots, X_n ; \mu_0,\mu_1,\tau)$ respectively denote the \emph{likelihoods} of the first $n$ observations under a model in $\cH_0$ and $\cH_1$.
High values of this statistic tend to indicate rejection of $\cH_0$.
%
By using the form of the likelihood for Bernoulli distributions, this statistic can be written with the binary relative entropy $\kl$, defined for $x,y\in[0,1]$ (with the usual convention that $t \log(t) = 0$ if $t=0$),
$\kl(x,y) := x \ln\left(\frac{x}{y}\right) + (1-x)\ln\left(\frac{1-x}{1-y}\right)$
%
Indeed, we show below
% in Appendix~\ref{app:6:GLR_with_kl}
that in any one-dimensional exponential family, we have
\begin{equation}\label{eq:6:secondDefGLRT}
    \log \GLR(n) = \sup_{s \in [2,n-1]} \left[s \times \kl\left(\widehat{\mu}_{1:s},\widehat{\mu}_{1:n}\right) + (n-s) \times \kl\left(\widehat{\mu}_{s+1:n},\widehat{\mu}_{1:n}\right)\right].
\end{equation}
%
where for $k \leq k'$, $\widehat{\mu}_{k:k'} := \frac{1}{k - k' + 1} \sum\limits_{l=k}^{k'} X_l$ denotes the average of the observations $X_l$ collected between the instants $k$ and $k'$.

\begin{smallproof}
    First, we consider the denominator in the expression of $\GLR(n)$ \eqref{eq:6:firstDefGLRT}, that is the $\sup$ on $\mu_0$.
    We have $\ell(X_1, \dots, X_n ; \mu_0) = \prod_{i=1}^n \ell(X_k ; \mu_0)$ by independence of the observations $X_k$,
    and $\ell(X_k ; \mu_0) = \mu_0^{X_k} (1-\mu_0)^{1-X_k}$ for Bernoulli distributions.
    Therefore, taking the logarithm gives
    \begin{align*}
        \log\ell(X_1, \dots, X_n ; \mu_0)
        &= \sum_{i=1}^n X_k \log(\mu_0) + (1-X_k) \log(1-\mu_0) \\
        &= \log(\mu_0) \times \left( \sum_{i=1}^n X_k \right) + \log(1-\mu_0) \times \left( n - \sum_{i=1}^n X_k \right) \\
        &= n \left( \widehat{\mu}_{1:n} \log(\mu_0) + (1 - \widehat{\mu}_{1:n}) \log(1-\mu_0) \right).
    \end{align*}
    %
    For a constant $a\in[0,1]$, let $h(x) := a \log(x) + (1-a) \log(1-x)$ on $(0,1)$,
    and we are trying to solve $\sup_{x\in[0,1]} h(x)$.
    If $a=0$ or $a=1$, $h$ is maximum at $x=a$.
    Now if $a\neq0$, As $h$ is of class $\cC^1$, we can just differentiate and find the root of its derivative:
    $h'(x) = a/x - (1-a)/(1-x)$, so $h'(x) = 0$ if and only if $x=a$.
    Thus in all cases, $\sup_{x\in[0,1]} h(x) = h(a)$.
    %
    Here, we have $a = \widehat{\mu}_{1:n}$, and thus we solve the $\sup_{\mu_0}$ optimization problem found in the denominator of the $\GLR(n)$ expression.
    By replacing $\mu_0 = \widehat{\mu}_{1:n}$, we obtained the following (unique) solution,
    \begin{equation}\label{eq:6:solutionPbOpt_for_1n}
        \sup_{\mu_0} \log\ell(X_1, \dots, X_n ; \mu_0) = n \left( \widehat{\mu}_{1:n} \log(\widehat{\mu}_{1:n}) + (1 - \widehat{\mu}_{1:n}) \log(1-\widehat{\mu}_{1:n}) \right).
    \end{equation}

@@

\begin{definition}\label{def:6:GLRDef}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
    The Bernoulli GLRT (B-GLRT) change point detector with threshold function $\beta(n,\delta)$ is the stopping time $\widehat{\tau}_{\delta}$ defined by
    %
    \begin{equation}\label{def:6:GLR}
        \widehat{\tau}_{\delta} := \inf \left\{ n \in \N^* : \sup_{s \in [2,n-1]} \left[s \times \kl\left(\widehat{\mu}_{1:s},\widehat{\mu}_{1:n}\right) + (n-s) \times \kl\left(\widehat{\mu}_{s+1:n},\widehat{\mu}_{1:n}\right)\right] \geq \beta(n,\delta)\right\}.
    \end{equation}
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

@@

%-----------------------------------------------------------------------------
\paragraph{False alarm probability.}\label{par:6:falseAlarm}
%
In Lemma~\ref{lem:6:FalseAlarm} below, we propose a choice of the threshold function $\beta(n,\delta)$ under which the probability that there exists a \emph{false alarm} under \iid{} data is small. To define $\beta$, we need to introduce the function $\cT$, defined for $x>0$ by
%
\begin{equation}\label{def:6:function_T}
    \cT(x) ~:=~ 2 \widetilde{h}\left(\frac{h^{-1}(1+x) + \ln(2\zeta(2))}{2}\right),
\end{equation}
where for $u \ge 1$ we define $h(u) = u - \ln(u)$ and its inverse $h^{-1}(u)$,
%
we define $\widetilde{h}(x) = e^{1/h^{-1}(x)} h^{-1}(x)$ if $x \ge h^{-1}(1/\ln (3/2))$ and $\tilde{h}(x) = (3/2) (x-\ln(\ln (3/2)))$ otherwise, for any $x \ge 0$,
and with the value $\zeta(2) = \pi^2 / 6$.
%
Even if it does not have a closed form expression, the function $\cT$ is easy to compute numerically.
%
The inverse $h^{-1}$ can be computed using $\mathcal{W}$, the Lambert $\mathcal{W}$ function \cite{Corless96}, which is the inverse of $x \mapsto x \exp(x)$, as $h^{-1}(x) = - \mathcal{W}(- \exp(-x))$.

@@

The \GLRklUCB{} algorithm can be viewed as a \klUCB{} algorithm allowing for some \emph{restarts} on the different arms. A restart happens when the B-GLRT change-point detector detects a change on the arm that has been played (line $9$).
%
To be fully specific, $\GLR_\delta(Z_1,\dots,Z_n) = \mathrm{True}$ if and only if
\begin{equation}\label{eq:whenDoesGLRklUCBrestart}
    \sup_{1 < s < n} \left[s \times \kl \left(\frac{1}{s}\sum_{i=1}^s Z_k , \frac{1}{n}\sum_{i=1}^n Z_k\right) + (n-s) \times \kl \left(\frac{1}{n-s}\sum_{i=s+1}^t Z_k , \frac{1}{n}\sum_{i=1}^n Z_k\right)\right] \geq \beta(n,\delta),
\end{equation}
%
with $\beta(n,\delta)$ defined in \eqref{def:6:beta}, or $\beta(n,\delta) = \ln(3n^{3/2}/\delta)$, as recommended in practice, see Section~\ref{sub:6:PracticalConsiderations}.
We define the (\klUCB{} like) index used by our algorithm, by denoting
$\tau_k(t)$ the last restart that happened for arm $k$ before time $t$,
$n_k(t) = \sum_{s=\tau_k(t)+1}^{t} \indic(A(s)=k)$
the number of selections of arm $k$, and
$\widehat{\mu}_k(t) = \frac{1}{n_k(t)} \sum_{s=\tau_k(t)+1}^{t}Y_{k,s} \indic(A(s)=i)$
their empirical mean (if $n_k(t)\neq0$).
%
With the exploration function $f(t) = \ln(t) + 3 \ln(\ln(t))$ if $t>1$ and $f(t)=0$ otherwise,
the index is defined using the binary relative entropy $\kl$ as
%
\begin{equation}\label{def:6:UCB}
    \UCB_k(t) := \max \Bigl\{ q\in[0,1] : n_k(t) \times \kl\left(\widehat{\mu}_k(t),q\right) \leq f(t - \tau_k(t)) \Bigr\}.
\end{equation}

@@

Recall that $\tau^{(i)}$ denotes the position of the $i$-th break-point and let $\mu_k^{(i)}$ be the mean of arm $k$ on the segment between the $i$ and $(i+1)$-th breakpoint:
$\forall t \in \{ \tau^{(i-1)}+1, \dots, \tau^{(i)} \}, \mu_k(t) = \mu_k^{(i)}$.
We also introduce $i^* = \arg\max_k \mu_k^{(i)} $ and the largest gap at break-point $i$ as $\Delta^{(i)} := \max_{k\in[K]} |\mu_k^{(i)} - \mu_k^{(i-1)}| >0$.

@@

Moreover, due to Proposition~\ref{prop:6:EnoughSamples}, $n_k(\tau^{(i)})$ lies in the interval $
\left[\left\lfloor \frac{\alpha}{K}\left(\tau^{(i)}-\widehat{\tau}^{(i-1)}\right)\right\rfloor,\left(\tau^{(i)}-\widehat{\tau}^{(i-1)}\right)\right]$.
Conditionally to $\cC^{(i-1)}$,
by using Assumption~\ref{ass:6:LongPeriodsGlobal},
we can prove that $d^{(i-1)} \leq (\tau^{(i)} - \tau^{(i-1)})/2$,
and thus we obtain furthermore that
%
\begin{eqnarray*}
    n_k(\tau^{(i)})& \in& \left\{ \left\lfloor \frac{\alpha}{2K} (\tau^{(i)}-\tau^{(i-1)} )\right\rfloor, \dots, \tau^{(i)}-\tau^{(i-1)} \right\} := \cI_k.
\end{eqnarray*}

>>>>

A \emph{piece-wise stationary bandit model} is characterized by a set of $K$ arms.
A (random) stream of rewards $(Y_{k,t})_{t\in\N^*}$ is associated to each arm $k \in [K]$. We assume that the rewards are bounded, and without loss of generality we assume that $Y_{k,t} \in [0,1]$.
We denote by $\mu_k(t) \eqdef  \bE[Y_{k,t}]$ the mean reward of arm $k$ at round $t$. At each round $t$, a decision maker has to select an arm $A(t)\in[K]$, based on past observation and receives the corresponding reward $r(t) = Y_{A(t),t}$.
At time $t$, we denote by $k_t^*$ an arm with maximal expected reward, \ie, $\mu_{k_t^*}(t) = \max_k \mu_k(t)$, called an optimal arm (possibly not unique).

@@

In the piece-wise \iid{} model, we furthermore assume that there is a (relatively small) number of \emph{breakpoints}, denoted by $\Upsilon_T \eqdef \sum_{t=1}^{T-1} \indic\left(\exists k\in[K]: \mu_k(t) \neq \mu_k(t+1)\right)$.
If we denote $\tau^{(0)} = 0$, we define the $i$-th breakpoint recursively by
$\tau^{(i)} = \inf\{t > \tau^{(i-1)} : \exists k : \mu_k(t) \neq \mu_k(t+1)\}$.
%
Hence for $t\in[\tau^{(i)} + 1,\tau^{(i+1)}]$, that is on any stationary segments, the rewards $(Y_{k,t})$ associated to each arm $k$ are \iid{} (hence the name of \emph{piece-wise stationary} problems).

@@

We define the \emph{number of change-points} on arm $k$,
$\NCk \eqdef \sum_{t=1}^{T-1} \indic\left(\mu_k(t) \neq \mu_k(t+1)\right)$,
for which it clearly holds that
$\NCk \leq \Upsilon_T$, but there can be an arbitrary difference between these two quantities for some arms. Letting $C_T \eqdef \sum_{k=1}^K \NCk$ be the total number of change-points on the arms, one can have $C_T \in \{ \Upsilon_T, \dots, K\Upsilon_T \}$.
We illustrate the two extreme cases in problems $1$ and $2$ presented in Figures~\ref{fig:6:Problem_1} and \ref{fig:6:Problem_2} below.

@@

If the samples $(X_t)$ were all drawn from a Bernoulli distribution, this change-point detection problem introduced above would reduce to a parametric sequential test of
$\cH_0 : (\exists \mu_0: \forall i\in\N, X_i \ \overset{\text{i.i.d.}}{\sim} \ \cB(\mu_0))$,
against the alternative
$\cH_1 : (\exists \mu_0 \neq \mu_1, \tau \in \N^*: \ \  X_1, \dots, X_\tau \ \overset{\text{i.i.d.}}{\sim} \ \cB(\mu_0) \ \ \text{and} \ \ X_{\tau+1}, X_{\tau+2}, \dots \ \overset{\text{i.i.d.}}{\sim} \ \cB(\mu_1))$.
%
The Generalized Likelihood Ratio statistic for this test is defined by
\begin{equation}\label{eq:6:firstDefGLRT}
    \GLR(n) \eqdef \frac{\sup\limits_{\mu_0,\mu_1,\tau < n}\ell(X_1, \dots, X_n ; \mu_0,\mu_1,\tau)}{\sup\limits_{\mu_0}\ell(X_1, \dots, X_n ; \mu_0)},
\end{equation}
%
where $\ell(X_1, \dots, X_n ; \mu_0)$ and $\ell(X_1, \dots, X_n ; \mu_0,\mu_1,\tau)$ respectively denote the \emph{likelihoods} of the first $n$ observations under a model in $\cH_0$ and $\cH_1$.
High values of this statistic tend to indicate rejection of $\cH_0$.
%
By using the form of the likelihood for Bernoulli distributions, this statistic can be written with the binary relative entropy $\kl$, defined for $x,y\in[0,1]$ (with the usual convention that $t \log(t) = 0$ if $t=0$),
$\kl(x,y) \eqdef x \ln\left(\frac{x}{y}\right) + (1-x)\ln\left(\frac{1-x}{1-y}\right)$
%
Indeed, we show below
% in Appendix~\ref{app:6:GLR_with_kl}
that in any one-dimensional exponential family, we have
\begin{equation}\label{eq:6:secondDefGLRT}
    \log \GLR(n) = \sup_{s \in [2,n-1]} \left[s \times \kl\left(\widehat{\mu}_{1:s},\widehat{\mu}_{1:n}\right) + (n-s) \times \kl\left(\widehat{\mu}_{s+1:n},\widehat{\mu}_{1:n}\right)\right].
\end{equation}
%
where for $k \leq k'$, $\widehat{\mu}_{k:k'} \eqdef \frac{1}{k - k' + 1} \sum\limits_{l=k}^{k'} X_l$ denotes the average of the observations $X_l$ collected between the instants $k$ and $k'$.

\begin{smallproof}
    First, we consider the denominator in the expression of $\GLR(n)$ \eqref{eq:6:firstDefGLRT}, that is the $\sup$ on $\mu_0$.
    We have $\ell(X_1, \dots, X_n ; \mu_0) = \prod_{i=1}^n \ell(X_k ; \mu_0)$ by independence of the observations $X_k$,
    and $\ell(X_k ; \mu_0) = \mu_0^{X_k} (1-\mu_0)^{1-X_k}$ for Bernoulli distributions.
    Therefore, taking the logarithm gives
    \begin{align*}
        \log\ell(X_1, \dots, X_n ; \mu_0)
        &= \sum_{i=1}^n X_k \log(\mu_0) + (1-X_k) \log(1-\mu_0) \\
        &= \log(\mu_0) \times \left( \sum_{i=1}^n X_k \right) + \log(1-\mu_0) \times \left( n - \sum_{i=1}^n X_k \right) \\
        &= n \left( \widehat{\mu}_{1:n} \log(\mu_0) + (1 - \widehat{\mu}_{1:n}) \log(1-\mu_0) \right).
    \end{align*}
    %
    For a constant $a\in[0,1]$, let $h(x) \eqdef a \log(x) + (1-a) \log(1-x)$ on $(0,1)$,
    and we are trying to solve $\sup_{x\in[0,1]} h(x)$.
    If $a=0$ or $a=1$, $h$ is maximum at $x=a$.
    Now if $a\neq0$, As $h$ is of class $\cC^1$, we can just differentiate and find the root of its derivative:
    $h'(x) = a/x - (1-a)/(1-x)$, so $h'(x) = 0$ if and only if $x=a$.
    Thus in all cases, $\sup_{x\in[0,1]} h(x) = h(a)$.
    %
    Here, we have $a = \widehat{\mu}_{1:n}$, and thus we solve the $\sup_{\mu_0}$ optimization problem found in the denominator of the $\GLR(n)$ expression.
    By replacing $\mu_0 = \widehat{\mu}_{1:n}$, we obtained the following (unique) solution,
    \begin{equation}\label{eq:6:solutionPbOpt_for_1n}
        \sup_{\mu_0} \log\ell(X_1, \dots, X_n ; \mu_0) = n \left( \widehat{\mu}_{1:n} \log(\widehat{\mu}_{1:n}) + (1 - \widehat{\mu}_{1:n}) \log(1-\widehat{\mu}_{1:n}) \right).
    \end{equation}

@@

\begin{definition}\label{def:6:GLRDef}
\begin{leftbar}[defnbar]  % XXX leftbar defnbar, comment if needed
    The Bernoulli GLRT (B-GLRT) change point detector with threshold function $\beta(n,\delta)$ is the stopping time $\widehat{\tau}_{\delta}$ defined by
    %
    \begin{equation}\label{def:6:GLR}
        \widehat{\tau}_{\delta} \eqdef \inf \left\{ n \in \N^* : \sup_{s \in [2,n-1]} \left[s \times \kl\left(\widehat{\mu}_{1:s},\widehat{\mu}_{1:n}\right) + (n-s) \times \kl\left(\widehat{\mu}_{s+1:n},\widehat{\mu}_{1:n}\right)\right] \geq \beta(n,\delta)\right\}.
    \end{equation}
\end{leftbar}  % XXX leftbar defnbar, comment if needed
\end{definition}

@@

%-----------------------------------------------------------------------------
\paragraph{False alarm probability.}\label{par:6:falseAlarm}
%
In Lemma~\ref{lem:6:FalseAlarm} below, we propose a choice of the threshold function $\beta(n,\delta)$ under which the probability that there exists a \emph{false alarm} under \iid{} data is small. To define $\beta$, we need to introduce the function $\cT$, defined for $x>0$ by
%
\begin{equation}\label{def:6:function_T}
    \cT(x) ~ \eqdef ~ 2 \widetilde{h}\left(\frac{h^{-1}(1+x) + \ln(2\zeta(2))}{2}\right),
\end{equation}
where for $u \ge 1$ we define $h(u) = u - \ln(u)$ and its inverse $h^{-1}(u)$,
%
we define $\widetilde{h}(x) = e^{1/h^{-1}(x)} h^{-1}(x)$ if $x \ge h^{-1}(1/\ln (3/2))$ and $\tilde{h}(x) = (3/2) (x-\ln(\ln (3/2)))$ otherwise, for any $x \ge 0$,
and with the value $\zeta(2) = \pi^2 / 6$.
%
Even if it does not have a closed form expression, the function $\cT$ is easy to compute numerically.
%
The inverse $h^{-1}$ can be computed using $\mathcal{W}$, the Lambert $\mathcal{W}$ function \cite{Corless96}, which is the inverse of $x \mapsto x \exp(x)$, as $h^{-1}(x) = - \mathcal{W}(- \exp(-x))$.

@@

The \GLRklUCB{} algorithm can be viewed as a \klUCB{} algorithm allowing for some \emph{restarts} on the different arms. A restart happens when the B-GLRT change-point detector detects a change on the arm that has been played (line $9$).
%
To be fully specific, $\GLR_\delta(Z_1,\dots,Z_n) = \mathrm{True}$ if and only if
\begin{equation}\label{eq:whenDoesGLRklUCBrestart}
    \sup_{1 < s < n} \left[s \times \kl \left(\frac{1}{s}\sum_{i=1}^s Z_k , \frac{1}{n}\sum_{i=1}^n Z_k\right) + (n-s) \times \kl \left(\frac{1}{n-s}\sum_{i=s+1}^t Z_k , \frac{1}{n}\sum_{i=1}^n Z_k\right)\right] \geq \beta(n,\delta),
\end{equation}
%
with $\beta(n,\delta)$ defined in \eqref{def:6:beta}, or $\beta(n,\delta) = \ln(3n^{3/2}/\delta)$, as recommended in practice, see Section~\ref{sub:6:PracticalConsiderations}.
We define the (\klUCB{} like) index used by our algorithm, by denoting
$\tau_k(t)$ the last restart that happened for arm $k$ before time $t$,
$n_k(t) = \sum_{s=\tau_k(t)+1}^{t} \indic(A(s)=k)$
the number of selections of arm $k$, and
$\widehat{\mu}_k(t) = \frac{1}{n_k(t)} \sum_{s=\tau_k(t)+1}^{t}Y_{k,s} \indic(A(s)=i)$
their empirical mean (if $n_k(t)\neq0$).
%
With the exploration function $f(t) = \ln(t) + 3 \ln(\ln(t))$ if $t>1$ and $f(t)=0$ otherwise,
the index is defined using the binary relative entropy $\kl$ as
%
\begin{equation}\label{def:6:UCB}
    \UCB_k(t) \eqdef \max \Bigl\{ q\in[0,1] : n_k(t) \times \kl\left(\widehat{\mu}_k(t),q\right) \leq f(t - \tau_k(t)) \Bigr\}.
\end{equation}

@@

Recall that $\tau^{(i)}$ denotes the position of the $i$-th break-point and let $\mu_k^{(i)}$ be the mean of arm $k$ on the segment between the $i$ and $(i+1)$-th breakpoint:
$\forall t \in \{ \tau^{(i-1)}+1, \dots, \tau^{(i)} \}, \mu_k(t) = \mu_k^{(i)}$.
We also introduce $i^* = \arg\max_k \mu_k^{(i)} $ and the largest gap at break-point $i$ as $\Delta^{(i)} \eqdef \max_{k\in[K]} |\mu_k^{(i)} - \mu_k^{(i-1)}| >0$.

@@

Moreover, due to Proposition~\ref{prop:6:EnoughSamples}, $n_k(\tau^{(i)})$ lies in the interval $
\left[\left\lfloor \frac{\alpha}{K}\left(\tau^{(i)}-\widehat{\tau}^{(i-1)}\right)\right\rfloor,\left(\tau^{(i)}-\widehat{\tau}^{(i-1)}\right)\right]$.
Conditionally to $\cC^{(i-1)}$,
by using Assumption~\ref{ass:6:LongPeriodsGlobal},
we can prove that $d^{(i-1)} \leq (\tau^{(i)} - \tau^{(i-1)})/2$,
and thus we obtain furthermore that
%
\begin{eqnarray*}
    n_k(\tau^{(i)})& \in& \left\{ \left\lfloor \frac{\alpha}{2K} (\tau^{(i)}-\tau^{(i-1)} )\right\rfloor, \dots, \tau^{(i)}-\tau^{(i-1)} \right\} \eqdef \cI_k.
\end{eqnarray*}
